\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}
\usepackage{tikz}

\frenchspacing 

\geometry{
  letterpaper,
  left = 0.5in,
  right = 0.5in,
  top = 0.6in,
  bottom = 0.6in
}

\hypersetup{
  colorlinks = true, 
  linkcolor = blue, 
  urlcolor  = blue,
  citecolor = blue, 
  anchorcolor = blue
}

%   CUSTOM STYLES  %
\thispagestyle{empty} % remove page number
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%   MACROS  %

\newcommand{\sectionStart}{
  \begin{itemize}[label={},leftmargin=0in]
}
\newcommand{\sectionEnd}{
  \end{itemize}
}
\newcommand{\head}[8]{
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{
      \textbf{{\color{black}{\LARGE {\underline{#1}}}}}
    }
    \vspace{5pt}\\
    \centerline{
      \href{mailto:#2}{\underline{#2}} $\mid$
      #3 $\mid$
      #4 : \href{#5}{\underline{#6}} $\mid$
      #7 : \href{#8}{\underline{#6}}
    }
  \end{tabular*}
  \vspace{-10pt}
}
\newcommand{\summaryText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    {#1}
  \end{addmargin}
}
\newcommand{\educationItem}[5]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{}}
    {#1 in \textbf{#2}}  & {#3}\\
    {\textit{#4}} & {#5}\\\vspace{-18pt}
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\skillItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    {\textbf{#1}: } & {#2}
  \end{tabular*}\vspace{-17pt}
}
\newcommand{\jobHeading}[3]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{\textbf{#1}} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{{\href{#1}{#2}} \textbf{#3}} & #4 \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\listStart}{\begin{itemize}}
\newcommand{\listEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\bulletItem}[1]{
  \item
  \small{
    {#1 \vspace{-1.8pt}}
  }
}
\newcommand{\udot}[1]{%
    \tikz[baseline=(todotted.base)]{
        \node[inner sep=0pt,outer sep=5pt] (todotted) {#1};
        \draw[dotted] (todotted.south west) -- ([xshift=10pt]todotted.south east);
    }%
}%

\newcommand{\declarationText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    {#1}
  \end{addmargin}
}

\begin{document}

%   HERO   %
\head
  {Raunak Jalan}
  {ronakjalan98@gmail.com}
  {+91-7984590915}
  {Github}
  {https://github.com/RaunakJalan}
  {RaunakJalan}
  {LinkedIn}
  {https://www.linkedin.com/in/raunak-jalan-dev/}

%   SUMMARY   %
\section{Summary}
\sectionStart
  \summaryText
  {Computer Science student with experience in developing web applications, machine learning models, desktop applications, automation bots using technologies such as Python, JavaScript (ES6), Shell Script and MongoDB. Seeking a \textbf{Software Developer Job} to leverage exemplary coding skills, analytical skills and leadership skills.}
\sectionEnd

%   EDUCATION   %
\section{Education}
\sectionStart
  \educationItem
    {Bachelor of Engineering} 
    {Computer Science} 
    {Expected June 2021}
    {Chandigarh University [Gharuan, Punjab]} 
    {8.68/10.0}
\sectionEnd

%   SKILLS   %
\section{Technical Skills}
\sectionStart
  \skillItem
    {Languages}
    {Python, C, C++, Java, Bash Scripting,HTML, CSS,  JavaScript}
  \skillItem
    {Frameworks}
    {Bootstrap, Flask, Selenium}
  \skillItem
    {Libraries}
    {Tkinter, OpenCV, Tensorflow, Keras, Scikit-Learn, Matplotlib}
  \skillItem
    {Tools}
    {Netbeans, Google Colab, Jupyter Notebook, Tableau, Bash, Git, \LaTeX\ }
  \skillItem
    {Databases}
    {IBM DB2, MySQL, MongoDB}
  \skillItem
    {Operating System}
    {Windows, Linux}
  \skillItem
    {Familiar with}
    {Flutter Development, Oracle SQL, REST APIs}
  \vspace{3pt}
\sectionEnd

%   PROJECTS   %
\section{Projects}
\sectionStart
  \projectHeading
    {https://github.com/RaunakJalan/LinkedIn_Automation}
    {LinkedIn Automation}
    {(Python, Selenium)}
    {March 2021 - Present}
  \listStart
    \bulletItem
      {In this project, a complete set of tasks are being automated for LinkedIn, from posting to profile scraping.}
  \listEnd  
  \projectHeading
    {https://rj-imagescrapper.herokuapp.com/}
    {Google Image Scraper}
    {(Python, Flask, Selenium, BeautifulSoup4)}
    {January 2021}
  \listStart
    \bulletItem
      {In this project, a flask application was created where, one can enter search keyword and number of images and application will scrape Google Images to get number of images for that input. A POST API is also created for this. It was then deployed on Heroku.}
    \bulletItem
      {Github: https://github.com/RaunakJalan/imageScrapper}
	\bulletItem
      {API: https://rj-imagescrapper.herokuapp.com/api/showImages}
  \listEnd
  \projectHeading
    {https://github.com/RaunakJalan/TensorFlow-Deployment-Course-Coursera/tree/master/Browser_Based_Model/Week_4/Rock_paper_scissor}
    {Rock Paper Scissor recognition using TensorflowJS}
    {(HTML, JavaScript, TensorflowJS)}
    {May 2020}
  \listStart
    \bulletItem
      {In this project, a complete set of data was recorded using a browser based model. And trained using TensorflowJS. Then it was predicted on browser.}
	\bulletItem
	  {Learned the basic and advanced concepts of TensorFlowJS.}
  \listEnd  
  \projectHeading
    {https://github.com/RaunakJalan/Virtual-Keyboard-OpenCV}
    {AR Virtual Keyboard}
    {(Python, OpenCV, Tkinter, PyAutoGUI)}
    {May 2019}
  \listStart
    \bulletItem
      {In this project, I used OpenCV library of Python to create a representation of a keyboard and track pad on screen and one can use the keyboard using camera and yellow color covered finger.}
    \bulletItem
      {Successfully learned to use Color Segmentation.}
  \listEnd
  \projectHeading
    {https://github.com/RaunakJalan/Credit-Card-Number-Identification}
    {Credit Card Digit Recognition}
    {(Python, OpenCV, TensorFlow)}
    {December 2018}
  \listStart
    \bulletItem
      {In this project, I used Computer Vision and CNN to create a model that successfully recognizes digits on a credit card. Complete data set was random and build by me using data augmentation.}
    \bulletItem
      {Learned how to create a data set.}
  \listEnd
  \projectHeading
    {https://rj-language-classification.herokuapp.com/}
    {Language Classification with Naive Bayes}
    {(Python, Scikit-Learn, Flask)}
    {October 2018}
  \listStart
    \bulletItem
      {In this project, with modification to various hyperparameters of Naive Bayes Algorithm a classification between Czech, English and Slovakian Language was made.}
	\bulletItem
	  {Learned the importance of Hyper Parameter alpha in Naive Bayes Algorithm.}
	\bulletItem
      {Github: https://github.com/RaunakJalan/Language-Classification-Naive-Bayes}
  \listEnd
\sectionEnd
  
%   EXPERIENCE   %
\section{Experience}
\sectionStart
  \jobHeading
    {SDET Intern}
    {October 2020 - Present}
    {Commvault Systems, India}
  \listStart
    \bulletItem
    {Automated multiple test cases for Command Center data agent IBM DB2.}
    \bulletItem
    {Achieved exposure towards \textbf{Commvault's} software architecture and its working.}
	\bulletItem
	{Achieved exposure towards \textbf{IBM DB2} database and its multiple configurations.}
	\bulletItem
	{Worked under an experienced SDET Engineer and got deep insights related to readability and optimization of code.}
  \listEnd
\sectionEnd

%   Certifications   %
\section{Certifications}
\sectionStart
    \bulletItem
    {\href{}{1. Completed Summer training in Machine Learning with A+ grade at Techienest}}
    \bulletItem
    {\href{https://coursera.org/share/692f14a73ae3b7188a460f07e6e58357}{2. Front End Web Development Specialization:Coursera}}
    \bulletItem
    {\href{https://coursera.org/share/3cb5be0a160a50819fb8c691a1e2bae2}{3. Deployment of ML models: Browser Based, Data Pipelines, Tensorflow Lite, Advance Deployment: Coursera}}
    \bulletItem
    {\href{https://www.udemy.com/certificate/UC-I146N8JD/}{4. Computer Vision with OpenCV Library using Python}}
    \bulletItem
    {\href{https://coursera.org/share/4a9d6e1dbc620cbbd834d4cc71a30985}{5. Google IT Automation with Python: Coursera}}
    \bulletItem
    {\href{https://drive.google.com/file/d/1faX-SPZJerRXQ-yNHDiWGLdW4N3rT11p/view?usp=sharing}{6. Cisco Linux Unhatched Certification}}
\sectionEnd


%   Awards   %
\section{Awards}
\sectionStart
  
    \bulletItem
    {\udot{3rd position Bug Finding Competition.}\qquad\qquad\qquad\qquad\udot{Technical Treasure Hunt Winner.}}
    \bulletItem
    {\ Techno Savvy Award in XII.\qquad\qquad\qquad\qquad\qquad\qquad\qquad\quad State Level IT quiz winner in XI.}
  
\sectionEnd

%   ExtraCurricular   %
\section{Extra Curricular Activities}
\sectionStart
  
    \bulletItem
    {1. Participated in TechFest Treasure Hunt.}
    \bulletItem
    {2. Created Posters for TechFest.}
    \bulletItem
    {3. Created Desktop App for TechFest Treasure Hunt.}
  
\sectionEnd

%   Declaration   %
\section{Declaration}
\sectionStart
  \declarationText
    {I do hereby declare that above information is true to best of my knowledge.}
  
\sectionEnd

\end{document}